Deterministic Scheduling of Periodic Messages in a Network by a SDN (deterministic) approach

### 2017-07-20 infocom/infocom.tex
modifs avant appel

      \todo{mettre le lemme sur la monotonie sans preuve?}

@@

     We show in the long version of this article that this problem is $\NP$-hard. 
      In Sec.~\ref{sec:PALL} we will study heuristics which try to solve the search version of PALL (computing an assignment), also denoted by PALL for simplicity.

@@

      \begin{center}
	\includegraphics[width=0.5\textwidth]{periode_petite.pdf}
      \end{center}
      \caption{Minimum period averaged over $1000$ random instances}
      \end{figure}

@@

      \WHILE{There is some non-assigned routes}
      \IF{${\cal H}$ is empty}
      \STATE t $\leftarrow $ min\_non\_assigned(eligible\_time)
      \STATE take $r_i$ the route with eligible\_time[$r_i$] = t
      \STATE 
      \ENDIF

@@

    \end{algorithmic}
    \end{algorithm}
    The function  min\_non\_assigned(eligible\_time) returns the lowest time in eligible\_time, for which the corresponding route is not assigned yet. The function update(t,free\_intervals) removes an interval of size $\tau$ beginning at t, which correspond to the message,  from free\_intervals.

@@

  \centering
     \hspace{-1.5cm} \includegraphics[width=0.4\textwidth]{departs_gp_21000.pdf}

      \caption{Success rate of different orders, $95\%$ load.}
          \end{figure}
\begin{figure}[H] 
          \includegraphics[width=0.5\textwidth]{departs_gp_25000.pdf}
      \caption{Success rate of different orders, $80\%$ load.}
           \label{fig:success30000}
     \end{figure}

>>>>

@@

 \begin{theorem}
Problem PALL is $\NP$-complete on some class of routed networks with specific parameters.
\end{theorem}
 \begin{proof}
 Problem $PRA$ is in $\NP$ since given an offset for each route in an assignment, it is easy to check in linear time in the number of arcs whether there are collisions.

  Let $H=(V,E)$ be an undirected graph and let $d$ be its maximal degree. We consider the problem to determine whether $H$ is arc-colorable
  with $d$ or $d+1$ colors. The arc coloring problem is $\NP$-hard~\cite{holyer1981np} and we reduce it to PRA to prove its $\NP$-hardness. To do that, we define from $H$ a routed network $(G,{\cal R})$.  
 The constraint of having no collision between the routes is equivalent to the fact that no two adjacent arcs have the same color. Therefore we have reduced arc coloring to PRA by a polynomial time transformation which concludes the proof. 
 \end{proof}

     The long version of this article contains the entire proof about the $\NP$-hardness of PALL. 
      In Sec.~\ref{sec:PALL} we will study heuristics which try to solve the search version of PALL (computing an assignment), also denoted by PALL for simplicity.

@@

      \begin{center}
	 \hspace{-0.5cm}\includegraphics[width=0.53\textwidth]{periode_petite.pdf}
      \end{center}
      \caption{Minimum period averaged over $1000$ random instances}
      \end{figure}

@@

      \WHILE{There is some non-assigned routes}
      \IF{${\cal H}$ is empty}
      \STATE $r_i$ $\leftarrow $ min\_non\_assigned(eligible\_time)
      \ENDIF

@@

    \end{algorithmic}
    \end{algorithm}
    The function  min\_non\_assigned(eligible\_time) returns the route with lowest time in eligible\_time, which is not assigned yet. The function update(t,free\_intervals) removes an interval of size $\tau$ beginning at t, which correspond to the message,  from free\_intervals.

@@

  \centering
     \hspace{-1.5cm} \includegraphics[width=0.4\textwidth]{departs_gp_21000.pdf}
\vspace{-0.75cm}
      \caption{Success rate of different orders, $95\%$ load.}
          \end{figure}
          \vspace{-1cm}
\begin{figure}[H] 
          \includegraphics[width=0.5\textwidth]{departs_gp_25000.pdf}
          \vspace{-1cm}
      \caption{Success rate of different orders, $80\%$ load.}
           \label{fig:success30000}
     \end{figure}
